Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''

### 2019-05-22 tex/v3/section_1_introduction.tex
small modif intro

A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\citep{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.  
Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
Furthermore, the dual of the entropic problem, referred to as {dual of Sinkhorn divergence}, was studied in~\cite{cuturinips13} and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
Therefore, the OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.

Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
A greedy version of Sinkhorn, called Greenkhorn algorithm and proposed in~\cite{altschulernips17}, allows to select columns and rows to be updated that most violate the constraints.                   
Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\citep{altschuler2018Nystrom}. 
Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\citep{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi Newton methods~\citep{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\citep{genevay2016stochOT,khalilabid2018}.

{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
is strongly related to a screening strategy when solving a \emph{Lasso}
problem in sparse supervised learning \citep{Ghaoui2010SafeFE}. Based on the fact
that a  transport plan resulting from an OT problem is sparse or presents a large
number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization.  
Within this global context, our contributions are the following:
\begin{itemize}
	  \setlength\itemsep{-0.1cm}

>>>>

A remedy to the heavy computation burden of OT lies in a prevalent approach referred as regularized OT~\citep{cuturinips13} and operates by adding an entropic regularization penalty to the original problem.  
Such a regularization guarantees a unique solution, since the objective function is strongly convex, and a greater computational stability.
%Furthermore, the dual of the entropic problem, referred to as {dual of Sinkhorn divergence}, was studied in~\cite{cuturinips13} and noticed that finding the dual solution was equivalent to finding two diagonal matrices that made a full matrix bistochastic.
More importantly, this regularized OT can be solved efficiently with celebrated matrix scaling algorithms, such as Sinkhorn's fixed point iteration method~\citep{sinkhorn1967,knight2008,kalantari2008}.

%Sinkhorn scaling for computing OT distances is a well studied problem in many recent works. 
%The main idea is to improve the matrix-vector operations that are the computational bottleneck of Sinkhorn’s algorithm. 
Several works have considered further improvements in the resolution of this regularized OT problem.
A greedy version of Sinkhorn, called Greenkhorn algorithm and proposed in~\cite{altschulernips17}, allows to select columns and rows to be updated that most violate the constraints.                   
Another approach based on low-rank approximation of the cost matrix using Nystrom method induces the Nys-Sink algorithm~\citep{altschuler2018Nystrom}. 
Other classical optimization algorithms have been considered to approximate the OT, for instance accelerated gradient descent~\citep{xie2018proxpointOT,dvurechensky18aICML,lin2019}, quasi Newton methods~\citep{blondel2018ICML,cuturi2016SIAM} and stochastic gradient descent~\citep{genevay2016stochOT,khalilabid2018}.

{In this paper, we propose a novel technique for accelerating the Sinkhorn algorithm when computing regularized OT distance between discrete measures. Our idea
is strongly related to a screening strategy when solving a \emph{Lasso}
problem in sparse supervised learning \citep{Ghaoui2010SafeFE}. Based on the fact
that a  transport plan resulting from an OT problem is sparse or presents a large
number of neglectable values \citep{blondel2018ICML}, our objective is to identify the  dual variables of an approximate Sinkhorn problem, that are smaller than a predefined threshold, and thus that can be safely removed before optimization while not altering too much the solution of the problem.  
Within this global context, our contributions are the following:
\begin{itemize}
	  \setlength\itemsep{-0.1cm}
